---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kyLogND

<!-- badges: start -->
<!-- badges: end -->

kyLogND is a set of utility functions to easily manipulate log normal distribution.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kenyam1979/kyLogND")
```
## Utility functions in kyLogND

* histLogND
* normalityCheckLogND
* meanIntervalLogND
* rlnorm2
* convertLogToMean
* convertLogToSD

`histLogND` draws histograms of the original distribution and log converted distribution with their mean and median.

```{r example}
library(kyLogND)

logND <- rlnorm2(100, mean=5, sd=2)
histLogND(logND)
```


`normalityCheckLogND` checks the normality of log transformed distribution using QQ-plot and Shaprio test.

```{r example2}
normalityCheckLogND(logND)
```

`meanIntervalLogND` calculates the interval estimate of mean for log normal distribution using Bootstrap method.
```{r example3}
meanIntervalLogND(logND, graphic=TRUE)
```
